Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-11 talk/vmil2012/paper.tex

Figure~\ref{fig:example} shows an example RPython function that checks
whether a number reduces to 1 with less than 100 steps of the Collatz process.
It uses an \lstinline{Even} and an \lstinline{Odd} class to box the numbers, to
make the example more interesting. If the loop in \lstinline{check_reduces} is
traced when \lstinline{a} is a multiple of four, the unoptimized
trace looks like in Figure~\ref{fig:unopt-trace}. The line numbers in the trace
correspond to the line numbers in Figure~\ref{fig:trace-log}.

@@

>>>>

Figure~\ref{fig:example} shows an example RPython function that checks
whether a number reduces to 1 with less than 100 steps of the Collatz process.
It uses an \lstinline{Even} and an \lstinline{Odd} class to box the numbers, to
make the example more interesting. If the loop in \lstinline{check_reduces} is
traced when \lstinline{a} is a multiple of four, the unoptimized
trace looks like in Figure~\ref{fig:unopt-trace}. The line numbers in the trace
correspond to the line numbers in Figure~\ref{fig:trace-log}. The resulting
trace repeatedly halves the current value and checks whether it is equal to
one, or odd. In either of these cases the trace is left via a guard failure.

@@

Figure~\ref{fig:trace-log} shows the optimized version of the trace in
Figure~\ref{fig:fig:unopt-trace}. Allocation removal has removed the
\lstinline{new} operation and other operations handling the boxes. The
operations handle unboxed numbers now.

Figure~\ref{fig:resume-data} sketches the symbolic frames of the first two
guards in the trace. The frames for \lstinline{check_reduces} and
\lstinline{Even.step} as well as the description of the allocation-removed
virtual instance of \lstinline{Even} are shared between the two guards.

\todo{fix labels in diagram}
